\begin{thebibliography}{1}

\bibitem{CMS} R. Adolphi et al. [CMS Collaboration] The CMS experiment at the CERN LHC,
JINST 3 (2008) S08004.

\bibitem{ATLAS}Aad, G. et al. [ATLAS Collaboration] The ATLAS Experiment at the CERN Large
Hadron Collider, JINST 3 (2008) S08003. 

\bibitem{scopertahiggs} S. Chatrchyan et al. [CMS Collaboration] Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC, Phys. Lett. B 716 (2012) 30 [arXiv:1207.7235 [hep-ex]].


\bibitem{ALICE}Aamodt, K. et al. [ALICE Collaboration] The ALICE experiment at the CERN
LHC JINST 3 (2008) S08002.

\bibitem{LHCb}Alves, A.Augusto, Jr. et al. [LHCb Collaboration] The LHCb Detector at the LHC
JINST 3 (2008) S08005.

\bibitem{LHCf}Adriani, O. et al. [LHCf Collaboration] The LHCf detector at the CERN Large
Hadron Collider JINST 3 (2008) S08006.

\bibitem{CMSTDR} CMS TDR.(da assegnare)

% LHC
% http://inspirehep.net/record/796247?ln=en

% Trigger L1
% http://inspirehep.net/record/541210?ln=en

% Papero HLT
% http://inspirehep.net/record/701526

% TDR tracker attuale + addendum
% TDR CMS tracker HL-LHC
% technical proposal upgrade

% papero tracciatura e vertexing
% http://inspirehep.net/record/1298029

% Alimentazione attuale
% https://cds.cern.ch/record/1091491/
% http://iopscience.iop.org/article/10.1088/1748-0221/5/07/C07009
% 



\bibitem{TesiGonnella} Tesi Gonnella.(da assegnare)

\bibitem{SerialPowering} D.B. Ta, T. Stockmanns, F. Huegging et al. ‘Serial powering: Proof of principle demonstration of a scheme for the operation of a large pixel detector at the LHC’. In: \textit{Nucl. Instrum. Meth.} A557 (2006), pp. 445–459. doi: 10.1016/j.nima.2005.11.115.

\bibitem{SLDO} M. Karagounis, D. Arutinov, M. Barbero et al. "An Integrated Shunt-LDO Regulator
for Serial Powered Systems". In: \textit{Proc. of the European Solid-State Device Conference,
ESSCIRC 2009 (2009)}, pp. 276–279. doi: 10.1109/ESSCIRC.2009.5325974.

\bibitem{RD53A} Garcia-Sciveres, Maurice (Lawrence Berkeley National Lab. (US)), "The RD53A Integrated Circuit" CERN-RD53-PUB-17-001.

\bibitem{YARR} http://yarr.readthedocs.io/en/latest/

\bibitem{BDAQ} https://gitlab.cern.ch/silab/bdaq53/wikis/home

\end{thebibliography}